書籍

### 2020-01-18 articles.Rmd
update
add number

- Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K (in press). Gambling symptoms, behaviors, and cognitive distortions in Japanese university students. Substance Abuse Treatment, Prevention, and Policy,

@@

- Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (2019). Associations between self-reported impulsivity and a latent variable of impulsive action constructed from three laboratory tasks. Journal of Experimental Psychopathology, 10, 3. doi: 10.1177/2043808719861894

@@

- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y. (2018). Depressive rumination and urgency have mutually enhancing relationships but both predict unique variance in future depression: A longitudinal study. Cogent Psychology, 5: 1450919.ß

- Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y. (2018). How do rumination and social problem solving intensify depression? A longitudinal study. Journal of Rational-Emotive & Cognitive-Behavior Therapy, 36, 1, 28-46.

- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T. A., & Yamawaki. (2018).  Enduring effects of a five-week behavioral activation program for subthreshold depression among late adolescents: an exploratory randomized controlled trial.  Neuropsychiatric Disease and Treatment , 14, 2633-2641.

@@

- Moriguchi, Y., Noda, T., Nakayashiki, K., Takata, Y., Setoyama, S., Kawasaki, S., Kunisato, Y., Mishima, K., Nakagome, K., Hanakawa, T. (2017). Validation of brain-derived signals in near-infrared spectroscopy through multivoxel analysis of concurrent functional magnetic resonance imaging. Human Brain Mapping, 38(10), 5274–5291.

- Yoshimura, S., Okamoto, Y., Matsunaga, M., Onoda, K., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2017). Cognitive behavioral therapy changes functional connectivity between medial prefrontal and anterior cingulate cortices, Journal of Affective Disorders, 15(208), 610-614.

@@

- Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, A. T., & Yamawaki. (2016). Behavioral activation for late adolescents with subthreshold depression: a randomized controlled trial. European Child & Adolescent Psychiatry, 25(11), 1171-1182.

- Hasegawa, A., Nishimura, H., Matsuda, Y., Kunisato, Y., Morimoto, H., & Adachi, M. (2016). Is trait rumination associated with the ability to generate effective problem solving strategies? Utilizing two versions of the Means-Ends Problem-Solving Test. Journal of Rational-Emotive & Cognitive-Behavior Therapy, 34, 14-30.

@@

- Tsukue, R., Okamoto, Y., Yoshino, A., Kunisato, Y., Takagaki, K., Takebayashi, Y., Tanaka, K., Konuma, K., Tsukue, I., & Yamawaki, S. (2015) Do Individuals with Alcohol Dependence Show Higher Unfairness Sensitivity? The Relationship Between Impulsivity and Unfairness Sensitivity in Alcohol-Dependent Adults. Alcoholism, clinical and experimental research, 39(10), 2016-2021.

- Nishiyama,Y., Okamoto, Y., Kunisato, Y., Okada, G., Yoshimura, S., Kanai, Y., Yamamura, T., Yoshino, A., Jinnin, R., Takagaki, K., Onoda, K., & Yamawaki, S. (2015) fMRI Study of Social Anxiety during Social Ostracism with and without Emotional Support. PLoS ONE 10(5): e0127426.

@@

- Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.

- Yoshino, A., Okamoto, Y., Kunisato, Y., Yoshimura, Y., Jinnin, R., Hayashi, Y., Kobayakawa, M., Doi, M., Oshita, K., Nakamura, R., Tanaka, K., Yamashita, H., Kawamoto, M., & Yamawaki, S. (2014). Distinctive spontaneous regional neural activity in patients with somatoform pain disorder: A resting-state fMRI preliminary study, Psychiatry Research: Neuroimaging, 221(3), 246-248.

- Toki, S., Okamoto, Y., Onoda, K., Matsumoto, T., Yoshimura, S., Kunisato, Y., Okada, G., Shishida, K., Kobayakawa, M., Fukumoto, T., Machino, A., Inagaki, M., Yamawaki, S. (2014). Hippocampal activation during associative encoding of word pairs and its relation to symptomatic improvement in depression: A functional and volumetric MRI study. Journal of Affective Disorder, 152, 462-467.

@@

- Yoshimura, S., Okamoto, Y., Onoda, K., Matsunaga, M., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2013). Cognitive behavioral therapy for depression changes medial prefrontal and ventral anterior cingulate cortex activity associated with self-referential processing. Social Cognitive and Affective Neuroscience, 9(4), 487-493.

- Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Kanai, Y., Ishikawa, S., & Sakano, Y. (2013). Preliminary assessment of the behavioral activation model in Japanese undergraduate students. Psychological Reports, 112(1), 47-59.

- Koseki, S., Noda., T., Yokoyama, S., Kunisato, Y., Ito, D., Suyama, H., Matsuda, T., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., Yoshida, S., Arima, K., Suzuki,S. (2013). The relationship between positive and negative automatic thought and activity in the prefrontal and temporal cortices: A multi-channel near-infrared spectroscopy (NIRS) study, Journal of Affective Disorders, 151(1), 352-359.

@@

- Kinoshita, A., Okamoto, Y., Okada, G., Demoto, Y., Kunisato, Y., Yoshimura, S., Onoda,K., Kamachi, M., Yamawaki, S. (2012) Sex differences in neural activation to ambiguous facial expression in happy and sad context, Perceptual and Motor Skills, 115(2), 349-359.

- Kunisato, Y., Okamoto, Y., Ueda, K., Onoda, K., Okada, G., Yoshimura, S., Suzuki, S., Samejima, K., Yamawaki, S. (2012) Effects of depression on reward based decision making and variability of action in probabilistic learning, Journal of Behavior Therapy and Experimental Psychiatry, 43, 1088-1094.

- Yoshino, A., Okamoto, Y., Onoda, K., Shishida, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G., Toki, S., Yamashita, H., Yamawaki, S. (2012) Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study, The Journal of Pain,13, 628-635.

- Demoto, Y., Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Tanaka, S. C., Schweighofer, N., Doya, K., Yamawaki, S. (2012) Neural And Personality Correlates of Individual Differences Related to the Effects of Acute Tryptophan Depletion on Future Reward Evaluation, Neuropsychobiology, 65, 55-64.

@@

- Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Nishiyama, Y., Yoshimura, S., Onoda, K., Toki, S., Yamashita, H., & Yamawaki, S. (2011) The effect of negative and positive emotionality on associative memory: An fMRI study, PLoS ONE, 6(9),e24862.

- Onoda, K., Okamoto, Y., Kunisato, Y., Aoyama, S., Shishida, K., Okada, G., Tanaka, SC., Schweighofer, N., Yamaguchi, S., Doya, K., & Yamawaki, S. (2011) Inter-individual discount factor differences in reward prediction are topographically associated with caudate activation, Experimental Brain Research, 212(4), 593-601.

- Kunisato, Y., Okamoto, Y., Okada, G., Aoyama, S., Nishiyama, Y., Onoda, K., Yamawaki, S. (2011)Personality traits and the amplitude of spontaneous low-frequency oscillations during resting state, Neuroscience Letters, 492(2), 109-113.

- Kunisato,Y., Okamoto, Y., Okada, G., Aoyama, S., Demoto, Y., Munakata, A., Nomura, M., Onoda, K., Yamawaki, S. (2011) Modulation of default - mode network activity by acute tryptophan depletion is associated with mood change：A resting state functional magnetic resonance imaging study. Neuroscience Research, 69, 129-134.

@@

- Matsunaga, M., Okamoto, Y., Suzuki, S., Kinoshita, A., Yoshimura, S., Yoshino, A., Kunisato, Y. & Yamawaki, S. (2010). Psychosocial functioning in patients with treatment-resistant depression after group cognitive behavioral therapy. Bmc Psychiatry, 10(1), 22.

- Yoshino, A., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G, & Shigeto, Y. (2010). Sadness enhances the experience of pain via neural activation in the anterior cingulate cortex and amygdala: An fMRI study. Neuroimage, 50(3), 1194-1201.

>>>>

### 2020

@@

- [28] Nishiguchi, Y., Sakamoto, J., Kunisato, Y., & Takano, K. (2019) Linear Ballistic Accumulator Modeling of Attentional Bias Modification Revealed Disturbed Evidence Accumulation of Negative Information by Explicit Instruction. Frontiers in Psychology,10, 2447.

- [27] Yokomitsu, K., Sakai, T., Irie, T., Tayama, J., Furukawa, H., Himachi, M., Kanazawa, J., Koda, M., Kunisato, Y., Matsuoka, H., Takada, T., Takahashi, F., Takahashi, T., & Osawa, K (2019). Gambling symptoms, behaviors, and cognitive distortions in Japanese university students. Substance Abuse Treatment, Prevention, and Policy, 14, 51.

- [26] Hasegawa, A., Somatori, K., Nishimura, H., Hattori, Y., & Kunisato, Y. (2019). Associations between self-reported impulsivity and a latent variable of impulsive action constructed from three laboratory tasks. Journal of Experimental Psychopathology, 10, 3. doi: 10.1177/2043808719861894

@@

- [25] Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y. (2018). Depressive rumination and urgency have mutually enhancing relationships but both predict unique variance in future depression: A longitudinal study. Cogent Psychology, 5: 1450919.ß

- [24] Hasegawa, A., Kunisato, Y., Morimoto, H., Nishimura, H., & Matsuda, Y. (2018). How do rumination and social problem solving intensify depression? A longitudinal study. Journal of Rational-Emotive & Cognitive-Behavior Therapy, 36, 1, 28-46.

- [23] Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, T. A., & Yamawaki. (2018).  Enduring effects of a five-week behavioral activation program for subthreshold depression among late adolescents: an exploratory randomized controlled trial.  Neuropsychiatric Disease and Treatment , 14, 2633-2641.

@@

- [22] Moriguchi, Y., Noda, T., Nakayashiki, K., Takata, Y., Setoyama, S., Kawasaki, S., Kunisato, Y., Mishima, K., Nakagome, K., Hanakawa, T. (2017). Validation of brain-derived signals in near-infrared spectroscopy through multivoxel analysis of concurrent functional magnetic resonance imaging. Human Brain Mapping, 38(10), 5274–5291.

- [21] Yoshimura, S., Okamoto, Y., Matsunaga, M., Onoda, K., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2017). Cognitive behavioral therapy changes functional connectivity between medial prefrontal and anterior cingulate cortices, Journal of Affective Disorders, 15(208), 610-614.

@@

- [20] Takagaki, K., Okamoto, Y., Jinnin, R., Mori, A., Nishiyama, Y., Yamamura, T., Yokoyama, S., Shiota, S., Okamoto, Y., Miyake, Y., Ogata, A., Kunisato, Y., Shimoda, H., Kawakami, N., Furukawa, A. T., & Yamawaki. (2016). Behavioral activation for late adolescents with subthreshold depression: a randomized controlled trial. European Child & Adolescent Psychiatry, 25(11), 1171-1182.

- [19] Hasegawa, A., Nishimura, H., Matsuda, Y., Kunisato, Y., Morimoto, H., & Adachi, M. (2016). Is trait rumination associated with the ability to generate effective problem solving strategies? Utilizing two versions of the Means-Ends Problem-Solving Test. Journal of Rational-Emotive & Cognitive-Behavior Therapy, 34, 14-30.

@@

- [18] Tsukue, R., Okamoto, Y., Yoshino, A., Kunisato, Y., Takagaki, K., Takebayashi, Y., Tanaka, K., Konuma, K., Tsukue, I., & Yamawaki, S. (2015) Do Individuals with Alcohol Dependence Show Higher Unfairness Sensitivity? The Relationship Between Impulsivity and Unfairness Sensitivity in Alcohol-Dependent Adults. Alcoholism, clinical and experimental research, 39(10), 2016-2021.

- [17] Nishiyama,Y., Okamoto, Y., Kunisato, Y., Okada, G., Yoshimura, S., Kanai, Y., Yamamura, T., Yoshino, A., Jinnin, R., Takagaki, K., Onoda, K., & Yamawaki, S. (2015) fMRI Study of Social Anxiety during Social Ostracism with and without Emotional Support. PLoS ONE 10(5): e0127426.

@@

- [16] Machino, A., Kunisato, Y., Matsumoto, T., Yoshimura, S., Ueda, K., Yamawaki, Y., Okada, G., Okamoto, Y., & Yamawaki, S (2014) Possible involvement of rumination in gray matter abnormalities in persistent symptoms of major depression: an exploratory magnetic resonance imaging voxel-based morphometry study, Journal of Affective Disorders, 168, 229-235.

- [15] Yoshino, A., Okamoto, Y., Kunisato, Y., Yoshimura, Y., Jinnin, R., Hayashi, Y., Kobayakawa, M., Doi, M., Oshita, K., Nakamura, R., Tanaka, K., Yamashita, H., Kawamoto, M., & Yamawaki, S. (2014). Distinctive spontaneous regional neural activity in patients with somatoform pain disorder: A resting-state fMRI preliminary study, Psychiatry Research: Neuroimaging, 221(3), 246-248.

- [14] Toki, S., Okamoto, Y., Onoda, K., Matsumoto, T., Yoshimura, S., Kunisato, Y., Okada, G., Shishida, K., Kobayakawa, M., Fukumoto, T., Machino, A., Inagaki, M., Yamawaki, S. (2014). Hippocampal activation during associative encoding of word pairs and its relation to symptomatic improvement in depression: A functional and volumetric MRI study. Journal of Affective Disorder, 152, 462-467.

@@

- [13] Yoshimura, S., Okamoto, Y., Onoda, K., Matsunaga, M., Okada, G., Kunisato, Y., Yoshino, A., Ueda, K., Suzuki, S., & Yamawaki, S. (2013). Cognitive behavioral therapy for depression changes medial prefrontal and ventral anterior cingulate cortex activity associated with self-referential processing. Social Cognitive and Affective Neuroscience, 9(4), 487-493.

- [12] Takagaki, K., Okajima, I., Kunisato, Y., Nakajima, S., Kanai, Y., Ishikawa, S., & Sakano, Y. (2013). Preliminary assessment of the behavioral activation model in Japanese undergraduate students. Psychological Reports, 112(1), 47-59.

- [11] Koseki, S., Noda., T., Yokoyama, S., Kunisato, Y., Ito, D., Suyama, H., Matsuda, T., Sugimura, Y., Ishihara, N., Shimizu, Y., Nakazawa, K., Yoshida, S., Arima, K., Suzuki,S. (2013). The relationship between positive and negative automatic thought and activity in the prefrontal and temporal cortices: A multi-channel near-infrared spectroscopy (NIRS) study, Journal of Affective Disorders, 151(1), 352-359.

@@

- [10] Kinoshita, A., Okamoto, Y., Okada, G., Demoto, Y., Kunisato, Y., Yoshimura, S., Onoda,K., Kamachi, M., Yamawaki, S. (2012) Sex differences in neural activation to ambiguous facial expression in happy and sad context, Perceptual and Motor Skills, 115(2), 349-359.

- [9] Kunisato, Y., Okamoto, Y., Ueda, K., Onoda, K., Okada, G., Yoshimura, S., Suzuki, S., Samejima, K., Yamawaki, S. (2012) Effects of depression on reward based decision making and variability of action in probabilistic learning, Journal of Behavior Therapy and Experimental Psychiatry, 43, 1088-1094.

- [8] Yoshino, A., Okamoto, Y., Onoda, K., Shishida, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G., Toki, S., Yamashita, H., Yamawaki, S. (2012) Sadness enhances the experience of pain and affects pain-evoked cortical activities: An MEG study, The Journal of Pain,13, 628-635.

- [7] Demoto, Y., Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Onoda, K., Munakata, A., Nomura, M., Tanaka, S. C., Schweighofer, N., Doya, K., Yamawaki, S. (2012) Neural And Personality Correlates of Individual Differences Related to the Effects of Acute Tryptophan Depletion on Future Reward Evaluation, Neuropsychobiology, 65, 55-64.

@@

- [6] Okada, G., Okamoto, Y., Kunisato, Y., Aoyama, S., Nishiyama, Y., Yoshimura, S., Onoda, K., Toki, S., Yamashita, H., & Yamawaki, S. (2011) The effect of negative and positive emotionality on associative memory: An fMRI study, PLoS ONE, 6(9),e24862.

- [5] Onoda, K., Okamoto, Y., Kunisato, Y., Aoyama, S., Shishida, K., Okada, G., Tanaka, SC., Schweighofer, N., Yamaguchi, S., Doya, K., & Yamawaki, S. (2011) Inter-individual discount factor differences in reward prediction are topographically associated with caudate activation, Experimental Brain Research, 212(4), 593-601.

- [4] Kunisato, Y., Okamoto, Y., Okada, G., Aoyama, S., Nishiyama, Y., Onoda, K., Yamawaki, S. (2011)Personality traits and the amplitude of spontaneous low-frequency oscillations during resting state, Neuroscience Letters, 492(2), 109-113.

- [3] Kunisato,Y., Okamoto, Y., Okada, G., Aoyama, S., Demoto, Y., Munakata, A., Nomura, M., Onoda, K., Yamawaki, S. (2011) Modulation of default - mode network activity by acute tryptophan depletion is associated with mood change：A resting state functional magnetic resonance imaging study. Neuroscience Research, 69, 129-134.

@@

- [2] Matsunaga, M., Okamoto, Y., Suzuki, S., Kinoshita, A., Yoshimura, S., Yoshino, A., Kunisato, Y. & Yamawaki, S. (2010). Psychosocial functioning in patients with treatment-resistant depression after group cognitive behavioral therapy. Bmc Psychiatry, 10(1), 22.

- [1] Yoshino, A., Okamoto, Y., Onoda, K., Yoshimura, S., Kunisato, Y., Demoto, Y., Okada, G, & Shigeto, Y. (2010). Sadness enhances the experience of pain via neural activation in the anterior cingulate cortex and amygdala: An fMRI study. Neuroimage, 50(3), 1194-1201.

### 2020-01-18 book.Rmd
add number

@@

- 国里愛彦・片平健太郎・沖村 宰・山下祐一(2019). 『計算論的精神医学: 情報処理過程から読み解く精神障害』  勁草書房 2019年1月25日 [Amazon.co.jp](https://www.amazon.co.jp/dp/432625131X/ref=cm_sw_r_tw_dp_U_x_KM7SCbP877MA8)

- 国里愛彦(2019). 第３章 「レスポンデント学習の理論モデル(pp.275-279)」，「レスポンデント学習の理論に基づくケースフォーミュレーション(pp.280-284)」下山晴彦・伊藤絵美・黒田美保・鈴木伸一・松田　修（編)『公認心理師技法ガイド：臨床の場で役立つ実践のすべて』文光堂 2019年3月26日　 [Amazon.co.jp](https://www.amazon.co.jp/dp/4830636262/ref=cm_sw_em_r_mt_dp_U_DL7SCbXZFBA0R)

@@

- 国里愛彦(2018). 「第14章　アセスメントにおける倫理的問題と法的問題」スーザン C. ウィストン(著)石川信一・佐藤寛・高橋史（監訳）『カウンセリングにおけるアセスメントの原理と適用』，金子書房，pp.343-364. [Amazon.co.jp](http://amzn.asia/d/7dg5Zgq)

- 国里愛彦(2018). 「第14章　いつになったら原稿を書くのか？: 執筆量モニタリングにおける変化点検出」『たのしいベイズモデリング 事例で拓く研究のフロンティア』豊田秀樹(編), 北大路書房, pp.149-159. [Amazon.co.jp](http://amzn.asia/d/2r9QFKj)

- 国里愛彦(2018). 「第3章7節　脳神経系の神経心理学的理解と認知機能の障害」　『公認心理師養成のための保健・医療系実習ガイドブック』鈴木伸一・田中恒彦・小林清香（編）,　北大路書房, pp.79-86. [Amazon.co.jp](http://amzn.asia/d/9TMdHZs)

- 国里愛彦(2018). 「第5章　健康関連のパーソナリティの測定と評価」　『健康心理学の測定法・アセスメント』鈴木伸一（編）, ナカニシヤ出版, pp.66-82. [Amazon.co.jp](http://amzn.asia/d/73OpXuw)

@@

- 国里愛彦(2017).「第24章　被予測変数がカウント変数の場合」』『ベイズ統計モデリング: R,JAGS, Stanによるチュートリアル 原著第2版』John K. Kruschke著，前田和寛・小杉考司監訳, 共立出版, pp.711-727.[Amazon.co.jp](http://amzn.asia/i6FoTrJ)

- 国里愛彦(2017). 「Chapter 2 心の源としての感覚・知覚・認知」・「Chapter 3 心の表れとしての行動」　『対人援助と心のケアに活かす心理学』鈴木伸一(編) , 有斐閣, pp.9-33. [Amazon.co.jp](http://amzn.asia/hZ4yMKn)

- 国里愛彦(2017). 「第５章　臨床心理学研究におけるサンプルサイズ設計」　『心理学のためのサンプルサイズ設計入門』　村井潤一郎・橋本貴充（共編）,　講談社，pp.86-106. [Amazon.co.jp](http://amzn.asia/0GOsHDM)

@@

- 国里愛彦 (2016). 脳画像検査　『公認心理師必携　精神医療・臨床心理の知識と技法』下山晴彦・中嶋義文(編)　医学書院　pp197-198. 2016/9/1 [Amazon.co.jp](http://amzn.asia/cWb3VuR)

- 国里愛彦 (2016). 「2.4 不適応の問題」&「2.5 心理的援助（心理的介入）」　『図説　現代心理学入門 [四訂版]』金城辰夫監修、山上精次・藤岡新治・下斗米淳(共編)　培風館 pp.56-65. 2016/3/30 [Amazon.co.jp](http://amzn.asia/3mCXXJN)

@@

- 国里愛彦(2015) 行動医学と生物統計学 p73-78「行動医学テキスト」日本行動医学会編集（編集委員：野村忍・堤明純・島津明人・中尾睦宏・吉内一浩）2015/10/25  [Amazon.co.jp](http://amzn.asia/cpANGJ5)

@@

- 『セラピストのための行動活性化ガイドブック＜うつ病を治療する10の中核原則＞』坂井誠・大野裕（監訳）創元社，2012年（担当した章：１章「序論　行動活性化の歴史」)  [Amazon.co.jp](http://amzn.asia/9yjCNHr)

- 『パーソナリティ心理学ハンドブック』　二宮克美・浮谷秀一・堀毛一也・安藤寿康・藤田主一・小塩真司・渡邊芳之（編）　福村出版　2013年（国里愛彦（著）「脳神経科学とパーソナリティ」, p85-91） [Amazon.co.jp](http://amzn.asia/cKObuiz)

- 『Encyclopedia of Behavioral Medicine』 「Type A」Kunisato Y．& Suzuki，S. Springer, 2013.  [Amazon.co.jp](http://amzn.asia/6FVAVlc)

- 『APA心理学大辞典』　Gary R. VandenBos (監修), 繁桝算男・四本裕子(監訳)　培風館, 2013年（一部翻訳）.[Amazon.co.jp](http://amzn.asia/eRIahSG)

@@

- 『うつを克服するための行動活性化練習帳：認知行動療法の新しい技法』大野裕・岡本泰昌（監訳）うつの行動活性化療法研究会（訳）　創元社，2012年（担当した章：１章)  [Amazon.co.jp](http://amzn.asia/9GW1z8K)

@@

- 『さあ！やってみよう　集団認知行動療法　うつ・不安への支援のために』集団認知行動療法研究会（監修） 医学映像教育センター　2011年　（松永美希・岡本泰昌・鈴木伸一・吉村晋平・国里愛彦・山脇成人(著) 「第２章 各施設の実践例: 広島大学病院精神神経科の場合」, p 20-30)  [Amazon.co.jp](http://amzn.asia/cyzswp7)

- 『うつ病の行動活性化療法：新世代の認知行動療法によるブレイクスルー』　熊野宏昭・鈴木伸一（監訳）日本評論社, 2011年 (担当した章：2章，6章，7章，8章，9章，10章，付録）  [Amazon.co.jp](http://amzn.asia/5Wp6dvL)

- 『うつ病の集団認知行動療法実践マニュアル：再発予防や復職支援に向けて』松永美希・吉村晋平・国里愛彦・鈴木伸一 (著) 鈴木伸一・岡本泰昌・松永美希（編）日本評論社　2011年  [Amazon.co.jp](http://amzn.asia/4jBendY)

- 『うつ病治療ハンドブック　診療のコツ』　大野裕（編）　金剛出版　2011年（国里愛彦・岡本泰昌（著）「行動活性化療法」, p 264-270）  [Amazon.co.jp](http://amzn.asia/72OLvVf)

@@

- 『さあ！はじめよう　うつ病の集団認知行動療法』　秋山剛・大野裕（監修）医学映像教育センター 2008年 (松永美希・鈴木伸一・岡本泰昌・木下亜紀子・上田一貴・小野田慶一・吉野敦雄・国里愛彦・山脇成人 (著) 「広島大学病院精神科における集団認知行動療法」, p146-149)  [Amazon.co.jp](http://amzn.asia/dn1cUT7)

>>>>

### 2020

@@

```{r eval=FALSE, include=FALSE}
後日追加

- 宗田卓史・国里愛彦・片平健太郎・沖村 宰・山下祐一(2019).　計算神経科学と精神医学：情報の観点から精神士官を見る　『Power Mook 精神医学の基盤』 Vol 3 No1, pp??- ??.  学樹書院
```

- [23]「診断ガイドライン(杣取恵太・国里愛彦，pp.632-633)」，「アウトカムの重要性(杣取恵太・国里愛彦，pp.658-659)」，「有害事象(国里愛彦，pp.660-661)」，「再現可能性(国里愛彦，pp.674-675)」『認知行動療法事典』丸善出版 2019年9月3日　[Amazon.co.jp](https://www.amazon.co.jp/dp/4621303821/ref=cm_sw_r_tw_dp_U_x_ySkBDbK4HP0P8)

- [22] 国里愛彦・片平健太郎・沖村 宰・山下祐一(2019). 『計算論的精神医学: 情報処理過程から読み解く精神障害』  勁草書房 2019年1月25日 [Amazon.co.jp](https://www.amazon.co.jp/dp/432625131X/ref=cm_sw_r_tw_dp_U_x_KM7SCbP877MA8)

- [21] 国里愛彦(2019). 第３章 「レスポンデント学習の理論モデル(pp.275-279)」，「レスポンデント学習の理論に基づくケースフォーミュレーション(pp.280-284)」下山晴彦・伊藤絵美・黒田美保・鈴木伸一・松田　修（編)『公認心理師技法ガイド：臨床の場で役立つ実践のすべて』文光堂 2019年3月26日　 [Amazon.co.jp](https://www.amazon.co.jp/dp/4830636262/ref=cm_sw_em_r_mt_dp_U_DL7SCbXZFBA0R)

@@

- [20] 国里愛彦(2018). 「第14章　アセスメントにおける倫理的問題と法的問題」スーザン C. ウィストン(著)石川信一・佐藤寛・高橋史（監訳）『カウンセリングにおけるアセスメントの原理と適用』，金子書房，pp.343-364. [Amazon.co.jp](http://amzn.asia/d/7dg5Zgq)

- [19] 国里愛彦(2018). 「第14章　いつになったら原稿を書くのか？: 執筆量モニタリングにおける変化点検出」『たのしいベイズモデリング 事例で拓く研究のフロンティア』豊田秀樹(編), 北大路書房, pp.149-159. [Amazon.co.jp](http://amzn.asia/d/2r9QFKj)

- [18] 国里愛彦(2018). 「第3章7節　脳神経系の神経心理学的理解と認知機能の障害」　『公認心理師養成のための保健・医療系実習ガイドブック』鈴木伸一・田中恒彦・小林清香（編）,　北大路書房, pp.79-86. [Amazon.co.jp](http://amzn.asia/d/9TMdHZs)

- [17] 国里愛彦(2018). 「第5章　健康関連のパーソナリティの測定と評価」　『健康心理学の測定法・アセスメント』鈴木伸一（編）, ナカニシヤ出版, pp.66-82. [Amazon.co.jp](http://amzn.asia/d/73OpXuw)

@@

- [16] 国里愛彦(2017).「第24章　被予測変数がカウント変数の場合」』『ベイズ統計モデリング: R,JAGS, Stanによるチュートリアル 原著第2版』John K. Kruschke著，前田和寛・小杉考司監訳, 共立出版, pp.711-727.[Amazon.co.jp](http://amzn.asia/i6FoTrJ)

- [15] 国里愛彦(2017). 「Chapter 2 心の源としての感覚・知覚・認知」・「Chapter 3 心の表れとしての行動」　『対人援助と心のケアに活かす心理学』鈴木伸一(編) , 有斐閣, pp.9-33. [Amazon.co.jp](http://amzn.asia/hZ4yMKn)

- [14] 国里愛彦(2017). 「第５章　臨床心理学研究におけるサンプルサイズ設計」　『心理学のためのサンプルサイズ設計入門』　村井潤一郎・橋本貴充（共編）,　講談社，pp.86-106. [Amazon.co.jp](http://amzn.asia/0GOsHDM)

@@

- [13] 国里愛彦 (2016). 脳画像検査　『公認心理師必携　精神医療・臨床心理の知識と技法』下山晴彦・中嶋義文(編)　医学書院　pp197-198. 2016/9/1 [Amazon.co.jp](http://amzn.asia/cWb3VuR)

- [12] 国里愛彦 (2016). 「2.4 不適応の問題」&「2.5 心理的援助（心理的介入）」　『図説　現代心理学入門 [四訂版]』金城辰夫監修、山上精次・藤岡新治・下斗米淳(共編)　培風館 pp.56-65. 2016/3/30 [Amazon.co.jp](http://amzn.asia/3mCXXJN)

@@

- [11] 国里愛彦(2015) 行動医学と生物統計学 p73-78「行動医学テキスト」日本行動医学会編集（編集委員：野村忍・堤明純・島津明人・中尾睦宏・吉内一浩）2015/10/25  [Amazon.co.jp](http://amzn.asia/cpANGJ5)

@@

- [10] 『セラピストのための行動活性化ガイドブック＜うつ病を治療する10の中核原則＞』坂井誠・大野裕（監訳）創元社，2012年（担当した章：１章「序論　行動活性化の歴史」)  [Amazon.co.jp](http://amzn.asia/9yjCNHr)

- [9] 『パーソナリティ心理学ハンドブック』　二宮克美・浮谷秀一・堀毛一也・安藤寿康・藤田主一・小塩真司・渡邊芳之（編）　福村出版　2013年（国里愛彦（著）「脳神経科学とパーソナリティ」, p85-91） [Amazon.co.jp](http://amzn.asia/cKObuiz)

- [8] 『Encyclopedia of Behavioral Medicine』 「Type A」Kunisato Y．& Suzuki，S. Springer, 2013.  [Amazon.co.jp](http://amzn.asia/6FVAVlc)

- [7] 『APA心理学大辞典』　Gary R. VandenBos (監修), 繁桝算男・四本裕子(監訳)　培風館, 2013年（一部翻訳）.[Amazon.co.jp](http://amzn.asia/eRIahSG)

@@

- [6] 『うつを克服するための行動活性化練習帳：認知行動療法の新しい技法』大野裕・岡本泰昌（監訳）うつの行動活性化療法研究会（訳）　創元社，2012年（担当した章：１章)  [Amazon.co.jp](http://amzn.asia/9GW1z8K)

@@

- [5] 『さあ！やってみよう　集団認知行動療法　うつ・不安への支援のために』集団認知行動療法研究会（監修） 医学映像教育センター　2011年　（松永美希・岡本泰昌・鈴木伸一・吉村晋平・国里愛彦・山脇成人(著) 「第２章 各施設の実践例: 広島大学病院精神神経科の場合」, p 20-30)  [Amazon.co.jp](http://amzn.asia/cyzswp7)

- [4] 『うつ病の行動活性化療法：新世代の認知行動療法によるブレイクスルー』　熊野宏昭・鈴木伸一（監訳）日本評論社, 2011年 (担当した章：2章，6章，7章，8章，9章，10章，付録）  [Amazon.co.jp](http://amzn.asia/5Wp6dvL)

- [3] 『うつ病の集団認知行動療法実践マニュアル：再発予防や復職支援に向けて』松永美希・吉村晋平・国里愛彦・鈴木伸一 (著) 鈴木伸一・岡本泰昌・松永美希（編）日本評論社　2011年  [Amazon.co.jp](http://amzn.asia/4jBendY)

- [2] 『うつ病治療ハンドブック　診療のコツ』　大野裕（編）　金剛出版　2011年（国里愛彦・岡本泰昌（著）「行動活性化療法」, p 264-270）  [Amazon.co.jp](http://amzn.asia/72OLvVf)

@@

- [1] 『さあ！はじめよう　うつ病の集団認知行動療法』　秋山剛・大野裕（監修）医学映像教育センター 2008年 (松永美希・鈴木伸一・岡本泰昌・木下亜紀子・上田一貴・小野田慶一・吉野敦雄・国里愛彦・山脇成人 (著) 「広島大学病院精神科における集団認知行動療法」, p146-149)  [Amazon.co.jp](http://amzn.asia/dn1cUT7)
